Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-10-18 ms/ms07_tables.tex
ENH

    \csvreader[separator=tab,
    tabular=crclcp{0.4\textwidth},
    late after last line=\\\hline,
    head,
    table head=\\\hline \bfseries Chrom. & \bfseries Pos (hg38) & \bfseries Cytoband & \bfseries RSID & \bfseries Gene marker& \bfseries Trait categories\\\hline,
    ]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_ms.tsv}{}% use head of csv as column names
        {\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi}% specify your coloumns here
    %
    \vspace{15pt}
    %
    \caption{
%        Represantive pleiotropic eQTLs involved in four GWAS categories in different cytobands.
%    The gene marker is the eQTL gene with the highest PubMed publication count.
%    The whole list is given in the Supplementary table ST2.
    }
    \label{tab:pleitropic_eqtls}
\end{table}

>>>>

    \csvreader[separator=tab,
    tabular=crclcp{0.4\textwidth},
    late after last line=\\\hline,
    head,
    table head=\\\hline \bfseries Chrom. & \bfseries Pos (hg38) & \bfseries Cytoband & \bfseries rsid & \bfseries Gene marker& \bfseries Trait categories\\\hline,
    ]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_ms.tsv}{}% use head of csv as column names
        {\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi}% specify your coloumns here
    %
    \vspace{15pt}
    %
    \caption{
%        Represantive pleiotropic eQTLs involved in four GWAS categories in different cytobands.
%    The gene marker is the eQTL gene with the highest PubMed publication count.
%    The whole list is given in the Supplementary table ST2.
    }
    \label{tab:pleitropic_eqtls}
\end{table}
